Neural dialogue act recognition with transformer pre-training

### 2019-04-06 abstract.tex

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models. \textbf{(How?)} For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.

>>>>

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models. \textbf{(How?)} For the datasets where no annotation for disfluencies is available, it can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
